---
title: "Initial Korean covid 19"
author: "Sandra Iovino"
date: "30 May 2024 Summer 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```

# Introduction 





### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020  
### This data was retrieved from a downloadable zip file from kaggle  

 Some of the data was uncoded for sex - sex must be just male or female
   
77 of the data entries were coded sex  as blank, so we omit these.  
  
state of a patient must be died or alive - we adjust that as well  

  
# Your Question - Is dying independent of sex?  

$H_0$ There is no difference in the rate of death between females and males.   


$H_A$ There is a difference between the rate of death between females and males.  


# Methods     
  
result is a categorical variable, sex is categorical  
   
result depends on sex, we use helper file   
  
cat~cat       


# Results 




## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```

This barchart shows that more males have died than females.    

  





  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

This numerical result show that 64% of males have died and 36% females have died. Which indicates that it almost double the amount of males that died than females. 


## Inferential results 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```



## Conclusions

